---
title: test
---

```{r, warning=FALSE}

library(forcats)
library(stringr)
library(ggridges)
library(tidyverse)
library(lubridate)
library(nycflights13)
library(colorspace)
library(Stat2Data)
library(ggrepel)

```


```{r fig-airquality, warning=FALSE, message=FALSE}
ggplot(mpg, aes(y = cty, x = displ, color = drv, fill = drv)) +
  geom_point(size = 3, shape = 21) +
  ylab("fuel economy (mpg)") +
  xlab("displacement (l)") +
  scale_color_manual(values=c("#202020", "#E69F00", "#56B4E9"),
                     name="drive train",
                     breaks=c("f", "r", "4"),
                     labels=c("FWD", "RWD", "4WD")) +
  scale_fill_manual(values=c("#20202080", "#E69F0080", "#56B4E980"),
                    name="drive train",
                    breaks=c("f", "r", "4"),
                    labels=c("FWD", "RWD", "4WD")) +
  theme(legend.position = c(.7, .8),
        plot.margin = margin(3, 7, 3, 1.5))
```

@fig-airquality illustrates the relationship between engine displacement (in liters) and fuel economy (in miles per gallon) across different drive train types—Front-Wheel Drive (FWD), Rear-Wheel Drive (RWD), and Four-Wheel Drive (4WD). Overall, there is a clear negative correlation between displacement and fuel economy: as engine displacement increases, fuel economy tends to decrease. This trend reflects the general principle that larger engines consume more fuel, resulting in lower miles per gallon.




